Secure Composition of Robust and Optimising Compilers

### 2023-07-10 popl/main.tex
rewrite little

% Fixing: Too many math alphabets used in version normal.
\newcommand\hmmax{0}
\newcommand\bmmax{0}
\documentclass[utf8,acmsmall,review,screen,dvipsnames]{acmart}

@@

These fixes alone are not enough to make this program secure in a robust setting, i.e., a malicious context could trigger a violation of either \gls{ms} or \gls{cct}.
Consider a program context that calls \texttt{strncpy} with an argument for \texttt{src} that points to uninitialized memory.
This leads to a series of reads from uninitialised memory, which is an immediate \gls{ms} issue that can have devastating real-world implications~\cite{uninit-0,uninit-1,uninit-2,uninit-3,uninit-4}.
An easy fix to sidestep this is to use non-nullable pointers as parameters instead, e.g., as presented in Cyclone~\cite{jim2002cyclone}.
With this, a secure compiler needs to ensure that no malicious target-level context can supply unitialised memory and thereby sidestep the guarantees of the source language, e.g., by inserting appropriate checks prior to entering the body of \texttt{strncpy} or using capabilities~\cite{michael2023mswasm}.
% a possible solution would be to compile to machiens with capabilities such as armorello or cheri
\end{example}

>>>>

% Fixing: Too many math alphabets used in version normal.
\newcommand\hmmax{0}
\newcommand\bmmax{0}
\documentclass[utf8,acmsmall,review,screen,dvipsnames,anonymous]{acmart}

@@

These fixes alone are not enough to make this program secure in a robust setting, i.e., a malicious context could trigger a violation of either \gls{ms} or \gls{cct}.
Consider a program context that calls \texttt{strncpy} with an argument for \texttt{src} that points to uninitialized memory.
This leads to a series of reads from uninitialised memory, which is an immediate \gls{ms} issue that can have devastating real-world implications~\cite{uninit-0,uninit-1,uninit-2,uninit-3,uninit-4}.
An easy fix to sidestep this is to use non-nullable pointers as parameters instead, e.g., as presented in Cyclone~\cite{jim2002cyclone}.
With this, a secure compiler needs to ensure that no malicious target-level context can supply unitialised memory and thereby sidestep the guarantees of the source language.
For example, if the target language is CHERI~\MK{cit} or MS-WASM~\cite{michael2023mswasm}\MK{check this} the compiler can ensure this by leavaraging the object capabilities. % , e.g., by inserting appropriate checks prior to entering the body of \texttt{strncpy} or using capabilities~\cite{michael2023mswasm}.
% a possible solution would be to compile to machiens with capabilities such as armorello or cheri
\end{example}
